---
title: "sampling"
author: "Lingyi Zhao, Sizhu Chen, Ye Yue"
date: "2018/10/29"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
###Install all packages
```{r}
library(dplyr)
library(tidyr)
library(stringr)
```

```{r}
###new train dataset
setwd('/Users/lingyizhao/Desktop/5291 proj')


###new train dataset

training<-read.csv("training.csv",stringsAsFactors = F)
testing<-read.csv("testing.csv",stringsAsFactors = F)
total<-rbind(training, testing)

total<-total[-c(3,4,5,10:16)]
#save(total, file="total.csv")
#save(total, file="total.RData")
songpool<-count(total, var=song_id)
names(songpool)<-c("song_id","fre")
```

Sepreate all genre
```{r}
########################################## Sizhu Chen #################################
usercount<-count(total, vars=total$msno)

top_10000<-function(df, col){
  temp_df<-df %>%
    arrange(desc(n))%>%
    print
  return(temp_df)
}


vvtop<-top_10000(usercount, usercount$n)[1:1000,]

merge<-subset(total, msno %in% vvtop$vars)

genre<-merge$genre_ids

cot<-rep(NA,length(genre))
for (i in 1:length(genre)){
  cot[i]<-str_count(genre[i],"\\|")+1
}

merge.expanded <- merge[rep(row.names(merge), cot),]
merge.expanded<-merge(merge.expanded, songpool,by="song_id" )
```

Change the weight of language after sepreation
```{r}
########################################## Ye Yue #################################
genre_split<-unlist(strsplit(genre,"\\|"))
merge.expanded$genre_ids<-genre_split 


weight<-unlist(lapply(cot,function(i){return(rep(1/i, i))} ))
merge.expanded$weight<-weight

# save(merge.expanded,file = "entire_cleaned_data.csv")
# save(merge.expanded,file = "entire_cleaned_data.RData")



 #vvtop<-top_10000(usercount, usercount$n)[1:100,]

```

Sample each user's song for 7:3, 70% for trainset, 30% for testset. Make sure all users both appear in trainset and testset. 
```{r}
########################################## Lingyi Zhao #################################
 merge<-subset(total, msno %in% vvtop$vars)

 #sepreate 7:3
 merge_new<-merge.expanded[order(merge.expanded[,2], decreasing = TRUE),]
 train<-data.frame()
 test<-data.frame()
 trainsong<-data.frame()
 users<-data.frame()

 for (i in vvtop$vars){
   train_number<-round(vvtop[which(vvtop$vars==i),2]*0.7)
   #print(train_number)
   test_number<-vvtop[which(vvtop$vars==i),2]-train_number$n
   song<-merge_new[which(merge_new$msno==i),1]
   #print(length(song))
   train<-sample(song,size = train_number$n)
   train<-data.matrix(train)
   #print(length(train))
   #train<-merge_new[which(merge_new$song_id %in% train),]
   user<-data.matrix(rep(i,train_number))
   users<-rbind(users,user)
   #print(nrow(users))
   trainsong<-rbind(trainsong, train)
   #print(nrow(trainsong))
 }
 trainset<-data.frame()
 trainset<-subset(merge_new, song_id %in% trainsong$V1 & msno %in% users$V1)
 
 testset<-data.frame()
 #testset<-merge_new[ !(merge_new$song_id %in% trainsong$V1 && merge_new$msno %in% users$V1), ]
 testset<-setdiff(merge_new, trainset)
 trainset$weight<-trainset$language*trainset$weight
 merge_new$weight<-merge_new$language*merge_new$weight
 save(trainset,file = "trainset.RData")
 save(testset,file = "testset.RData")
```

Get table for each user's (genre, language, artist) and find top genre and language and artist
```{r}
########################################## Lingyi Zhao #################################
top_features<-data.frame()
top_genres<-data.frame()
top_languages<-data.frame()
top_artists<-data.frame()
#list<-unique(trainset$msno)
#names(top_feature)<-c("User","top_genre", "top_language","top_artist")
for (h in vvtop$vars){
  top_genre<-as.numeric(names(sort(table(trainset$genre_ids[trainset$msno==h]), decreasing = TRUE))[1])
  top_genres<-rbind(top_genres,top_genre)
  
  top_language<-as.numeric(names(sort(table(trainset$language [trainset$msno==h]), decreasing = TRUE))[1])
  top_languages<-rbind(top_languages,top_language)
  
  #top_artist<-as.numeric(names(table(trainset$artist_name[trainset$msno==h]))[1])
  #top_artists<-rbind(top_artists,top_artist)
}
top_features<-cbind(vvtop$vars ,top_genres, top_languages)
names(top_features)<-c("Users","genre","language")
```

Recommend music based on (genre, language, artist) and users should not listen these music before
```{r, warning=FALSE}
########################################## Lingyi Zhao #################################
recommends<-data.frame()
recommend_musicset<-data.frame()
allmusic<-songpool[order(songpool$fre),]
listenedmusic<-data.frame()
allpairs<-data.frame()
colnames(allmusic)<-c("music", "fre")
repusers<-data.frame()
r<-1
for (g in top_features$Users){
  listenedmusic<-data.frame(unique(trainset$song_id[trainset$msno==g]))
  names(listenedmusic)<-c("music")
  recommend_musicset<-data.frame(setdiff(allmusic$music, listenedmusic$music))
  colnames(recommend_musicset)<-c("music")
  allpair<-subset(merge_new, song_id %in% recommend_musicset$music & msno==g)
  gen<-top_features$genre[top_features$Users==g]
  lang<-top_features$language[top_features$Users==g]
  recommend<-subset(allpair, allpair$genre_ids == gen & allpair$language == lang)
  if(nrow(recommend)==0){
    recommend<-allpair$song_id[order(allpair$fre, decreasing = TRUE)][1:10]
  }
  else{
  recommend<-recommend$song_id[order(recommend$fre, decreasing = TRUE)][1:10]}
  for (d in 1:10){
    recommends[r,1]<-as.character(recommend[d])
    r<-r+1
  }
  
  repuser<-data.matrix(rep(g, 10))
  repusers<-rbind(repusers, repuser)
}

recommends_final<-cbind(repusers,recommends$V1)
names(recommends_final)<-c("Users","recommend_music")
save(recommends_final,file = "recommends_final.RData")
```

Calculate test error
```{r}
########################################## Lingyi Zhao #################################
r<-1
score<-data.frame()
recommend_to_user<-data.frame()
#testsong<-data.frame()
for (p in unique(recommends_final$Users)){
  testsong<-data.frame(testset$song_id[testset$msno==p])
  recommend_to_user<-data.frame(recommends_final$recommend_music[recommends_final$Users==p])
  colnames(testsong)<-c("music")
  colnames(recommend_to_user)<-c("music")
  if (any(recommend_to_user$music %in% testsong$music)){
    score[r,1]<-sum(recommend_to_user$music%in% testsong$music)
    #score<-nrow(right)
  }
  else{
    score[r,1]<-0
  }
  r<-r+1
}
sum(score)
testerror<-(10-sum(score)/1000)/10
testerror
```

